checkData

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(review_harmonized = case_when(
           review_harmonized == "NO, This correspondence is published at the discretion of the Editor-in-Chief and the Associate Editors" ~ "NO",
           review_harmonized == "NOT STATED, The guidelines discuss peer review, but it appears that this discussion isn't relevant to commentary articles." ~ "NOT STATED",
           review_harmonized == "UNCLEAR (provide detail in the 'other' section below), It 'may' be sent for independent review: 'Matters Arising submissions that meet the journal’s criteria are sent to the authors of the original paper for a formal response. The comments and formal response may then be sent to independent referees.'" ~ "YES",
           TRUE ~ review_harmonized
         )) 
```

>>>>

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(review_harmonized = case_when(
           review == "NO, This correspondence is published at the discretion of the Editor-in-Chief and the Associate Editors" ~ "NO",
           review == "NOT STATED, The guidelines discuss peer review, but it appears that this discussion isn't relevant to commentary articles." ~ "NOT STATED",
           review == "UNCLEAR (provide detail in the 'other' section below), It 'may' be sent for independent review: 'Matters Arising submissions that meet the journal’s criteria are sent to the authors of the original paper for a formal response. The comments and formal response may then be sent to independent referees.'" ~ "YES",
           TRUE ~ review
         )) 
```
